\documentclass[11pt,letterpaper,sans]{moderncv}

% adjust the page margins
\usepackage[scale=0.9]{geometry}
\usepackage{fontspec}
\usepackage{fontawesome5}
\usepackage{xpatch}
% if you want to change the width of the column with the dates
%\setlength{\hintscolumnwidth}{3cm}                
% for the 'classic' style, if you want to force the width allocated to your name
% and avoid line breaks. be careful though, the length is normally calculated to
% avoid any overlap with your personal info; use this at your own typographical
% risks...
%\setlength{\makecvtitlenamewidth}{10cm}           

\moderncvstyle{classic}
\moderncvcolor{purple}
\moderncvicons{awesome}

% personal data
\name{Bailey}{Bjornstad}
\title{Data Engineer and Analyst at unumAI}
% optional; the "postcode city" and "country" arguments can be omitted or
% provided empty
\address{444 East 19th Avenue Apt C405}{Denver, CO 80203}
% optional; the optional "type" of the phone can be "mobile" (default), "fixed"
% or "fax"
\phone[mobile]{+1~(760)~419~9148}
% optional
\email{baileybjornstad@gmail.com}
\social[linkedin]{bailey-bjornstad}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}

%-----       letter       ---------------------------------------------------------
% recipient data
\recipient{Ezoic Recruitment}{Ezoic\\6023 Innovation Way\\Carlsbad, CA 92009}
\date{\today}
\opening{Dear Hiring Manager:}
\closing{Sincerely,}
% use an optional argument to use a string other than "Enclosure", or redefine
% \enclname
\makelettertitle



\makeletterclosing

\clearpage

% remove periods at the end of lines.
\xpatchcmd{\cventry}{.\strut}{\strut}{}{}

%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Experience}
\subsection{Data Engineering and Analysis}
\cventry{2020--2022}{Data Engineer and Analyst}{unumAI}{Denver, CO}{}{
    Developed company data management software from mathematical specifications
    with focus on collection and processing of Google Trends Search data for
    political prediction and issue analysis research.
\begin{itemize}
    \item   Led company technical development through implementation of most
        company methodologies using Python, SQL, and Azure to facilitate easy
        collection, transformation, storage, and PowerBI presentation of Google
        Trends search data.
    \item   Used asynchronous request tooling in tandem with Azure Function
        Applications to increase data collection speeds by orders of magnitude
        at very low cost.
    \item   Integrated Azure tooling for company data maintenance to provide a
        foundational and extensible software platform for data integration that
        is accessible to those not necessarily familiar with programming methods
        or languages.
    \item   Wrote complex DAX code to tackle interactive visual measurement and
        display of Google Trends Search data across all client contexts.
    \item   Assisted company clients during product and project pitch
        presentations by clarifying technical aspects of estimation and
        analysis, or with outright presentation of material to prospective
        client teams.
    \item   Exhibited a strong ability to think quickly and understand new
        domain specific knowledge across fields as applied to a specific
        question or technical problem.
    \item Demonstrated self-sufficiency in a remote environment, managing
        expectations and workload on a team of only two people in a fast paced
        environment and with many responsibilities.
\end{itemize}}
\cventry{2019--2020}{Data Management and Analytics Specialist}{Bright Event
Rentals}{San Diego, CA}{}{Assisted company analytics endeavors through
CyberQuery programming on database of transactions, rental equipment, and
customers
\begin{itemize}
    \item   Wrote customized and automated database queries using CyberQuery to
        improve rental business analytics and reporting
    \item   Facilitated major revenue generation by using historical data to
        optimize sales of equipment rental protection policies
    \item   Classified customers in terms of business strategy goals using data
        to identify inconsistencies between company locations
\end{itemize}}
\subsection{Mathematics}
\cventry{2017--2019}{Teaching Assistant}{Northwestern University}{Evanston,
IL}{}{Assisted professors of six multivariable and single-variable undergraduate
calculus classes by running discussion sections and working one-on-one with
students.}
\cventry{2017--2018}{Peer Tutor}{Northwestern University}{Evanston,
IL}{}{Assisted fellow undergraduates of Northwestern University with a variety
of math courses in a weekly, drop-in setting.}
\cventry{Summer 2017}{Independent Research in Math}{Northwestern
    University}{Evanston, IL}{}{Developed a concept of \emph{mathematical
        fragility} in birth and death stochastic processes.
\begin{itemize}
    \item   Used \texttt{Python} and accompanying analytical tools to develop a
        preliminary model through simulation of birth and death stochastic
        processes.
    \item   Mathematically analyzed examples to verify properties of these
        preliminary models.
    \item   Abstractly developed these preliminary models using mathematical
        tools from probability to draw out quantities that describe the
        fragility of a process.
\end{itemize}}
\cventry{Fall 2016}{Research Assistant}{Northwestern University}{Evanston,
IL}{}{Aided research on inquiry-based approaches to math education by recording
classes and documenting student interactions in a novel classroom setting.}
% \subsection{Miscellaneous}
% \cventry{Summer 2016}{Research Assistant}{University of California San
% Diego}{San Diego, CA}{}{Developed a reusable analysis pipeline for single-cell
%     RNA sequencing data used in research on middle-ear infections.
% \begin{itemize}
%     \item   Worked with the \texttt{R} programming language to analyze data sets
%         for intuitive groupings.
%     \item   Wrote a series of scripts designed to process and analyze data sets
%         to look for differences in groupings.
%     \item   Created visualizations of data in order to better understand the
%         differences between these groups.
% \end{itemize}}
\clearpage

\section{Education}
\cventry{2015--Present}{Mathematics}{Northwestern University}{Evanston, IL}{GPA:
$3.7/4.0$}{Undergraduate major in Math with emphasis on advanced classes where
    possible.\newline Relevant Courses:
\begin{itemize}
    \item   \emph{ISP Math} --- A three quarter intensive course covering
        multivariable calculus, ordinary differential equations, and linear
        algebra.
    \item	  \emph{Foundations of Higher Math} --- A single quarter course on the
        standards of mathematical proof.
    \item	  \emph{MENU Real Analysis} --- A three quarter intensive course that
        rigorously develops calculus, including measure theory.
    \item	  \emph{MENU Abstract Algebra \& Abstract Algebra} --- Two quarters of
        an intensive course devoted to the study of groups and rings, followed
        by a one quarter course on Galois Theory.
    \item   \emph{Other Computer Science \& Applied Math} --- Various computer
        science and applied math courses covering topics including data
        structures, \texttt{Python} implementations of fundamental algorithms
        from machine learning, and computational neuronal modeling.
\end{itemize}}
\cventry{}{Music Technology}{Northwestern University}{Evanston,
IL}{}{Undergraduate minor in Music Technology, with coursework focused on
synthesis and analysis of electronic music. In a degree project, co-designed and
prototyped a laser harp digital music interface.}
\cventry{2011--2015}{High School Diploma}{Pacific Ridge School}{Carlsbad,
CA}{GPA: $4.0/4.0$}{Relevant Achievements:
\begin{itemize}
    \item   \emph{Captain of Robotics Team} --- Led a team of peers to multiple podium finishes in First
        Tech Challenge robotics competitions.
    \item   \emph{Theatrical Technical Director} --- Organized and produced the technical side of yearly
        musicals and plays, particularly with regards to audio.
\end{itemize}}

\section{Awards}
\cventry{May 2016}{Excellence in Mathematics by a First-Year
Student}{Northwestern University}{Evanston, IL}{}{Award given to students who
display strong achievement in a number of advanced mathematics courses offered
at Northwestern University.}
\cventry{May 2019}{Certificate of Recognition for Service as an Undergraduate
Teaching Assistant}{Northwestern University}{Evanston, IL}{}{A certificate given
to senior teaching assistants who dedicated their distinguished skills by
continually serving Northwestern's math department.}

\section{Computer Skills}
\cvitemwithcomment{Programming}{\texttt{Python, SQL, R}}{Expert}
\cvitemwithcomment{Cloud Services}{Azure}{Proficient}
\cvitemwithcomment{Statistics}{\texttt{Numpy, Pandas}}{Expert}
\cvitemwithcomment{BI/Visualization}{Microsoft Power BI,
\texttt{Matplotlib}}{Expert}
\cvitemwithcomment{Typesetting}{{\fontfamily{cmr}\selectfont \LaTeX}}{Expert}
\cvitem{Linux}{Built and maintain a customized installation of Arch Linux as my
daily operating system. Familiar with many other distributions as well.}

\section{Hobbies and Interests}
\cvitem{Radio DJ}{Host of \textit{Non-Euclidean Space}, \textit{Excitotoxicity},
and \textit{Late Night Geometries} on WNUR 89.3 FM, with focus on electronic
music of different geometries.}
\cvitem{MTG}{Have played the trading card game \textit{Magic: The Gathering} at
a competitive level.}
\cvitem{Cooking}{In the kitchen, a devotee of \emph{Good Eats}'s Alton Brown and
publications \emph{Serious Eats} and \emph{Cook's Illustrated}.}

\clearpage

\section{References}
\cvitem{Skylar White}{\emph{unumAI}\newline
CEO/Founder\newline
jskylarwhite@gmail.com\newline
Director and Supervisor at unumAI}
\cvitem{Lauren Beaver}{\emph{KPMG}\newline
Azure Integrations Specialist\newline
laurenbeaver5656@gmail.com\newline
Advisor at unumAI on Azure Integration}
\cvitem{Dr. Nick Webster}{\emph{University of California San Diego}\newline
Professor of Medicine\newline
nwebster@ucsd.edu\newline
Advisor on RNA Sequencing Research Project}

\end{document}
