% remove periods at the end of lines.
\xpatchcmd{\cventry}{.\strut}{\strut}{}{}

\makecvtitle
\vspace*{-5mm}

% ------------------------------------------------------------------------------
% ---- Experience Section
% ------------------------------------------------------------------------------
\section{Experience --- Engineering, Analytics, and Data Management}
\cventry{2020--2022}{Data Engineer and Analyst}{unumAI}{Denver, CO}{}{
    Developed company data management software from mathematical specifications
    with focus on collection and processing of Google Trends Search data for
    political prediction and issue analysis research.
\begin{itemize}
    \item   Led company technical development through implementation of most
        company methodologies using advanced Python, DAX, Azure, and SQL, to
        facilitate easy collection, transformation, warehousing, and PowerBI
        presentation of Google Trends Search data. The unumAI internal
        \emph{pyunum} module contains Python interfaces to custom Google Trends
        data collection and transformation methods.
    \item   Integrated Azure tooling for company data maintenance to provide a
        foundational and extensible software platform for data integration that
        is accessible to those not necessarily familiar with programming methods
        or languages.
    \item   Used asynchronous request tooling in tandem with Azure Function
        Applications to increase data collection speeds by orders of magnitude
        at very low cost.
    \item   Assisted company clients during product and project pitch
        presentations by clarifying technical aspects of methodology, or with
        outright presentation of material to prospective client teams when
        needed.
    \item   Exhibited a strong ability to think quickly and understand new
        domain specific knowledge across fields as applied to a specific
        question or technical problem.
    \item   Demonstrated self-sufficiency in a remote environment, managing
        expectations and workload on a team of only two people in a fast-paced,
        early-stage start-up environment, with rapidly evolving project
        directives that result from changing client needs.
    \item   Some of the clients served at unumAI: Children's Hospital Colorado,
        Partners for Children's Mental Health, Missouri Department of Health
        and Senior Services, Siena College Research Institute, and
        political campaigns. A comprehensive list can be found at
        \href{https://www.unumai.org}{unumai.org}.
\end{itemize}}
\cventry{2019--2020}{Data Management and Analytics Specialist}{Bright Event
Rentals}{San Diego, CA}{}{Assisted company analytics endeavors through
    CyberQuery programming on databases of transactions, rental equipment, and
    customers
\begin{itemize}
    \item   Wrote customized and automated database queries using CyberQuery to
        improve rental business analytics and reporting.
    \item   Facilitated major revenue generation by using historical data to
        optimize sales of equipment rental protection policies.
    \item   Classified customers in terms of business strategy goals using data
        to identify inconsistencies between company locations.
\end{itemize}}

% ------------------------------------------------------------------------------
% ---- Computer Skills Section
% ------------------------------------------------------------------------------
\section{Computer Skills}
\cvitemwithcomment{Development}{\texttt{Python}, Jupyter, Azure*, \texttt{SQL*,
R, Git}, Unix Shell}{Expert: $\sim 6+$ years | $*\sim 3+$ years}
\cvitemwithcomment{libraries.py}{\texttt{stdlib}, Pandas, NumPy,
\texttt{Matplotlib}}{Expert: $\sim 6+$ years}
\cvitemwithcomment{}{SqlAlchemy*, \texttt{asyncio/aiohttp}*}{Advanced+: $*\sim 3$ years}
\cvitemwithcomment{BI/Visualization}{Microsoft Power BI, \texttt{DAX}}{Expert:
$\sim 3$ years}
\cvitemwithcomment{Typesetting}{{\fontfamily{cmr}\selectfont \LaTeX}}{Expert:
$\sim 5$ years}
\cvitem{Linux}{Built and maintain a customized installation of Arch Linux as my
daily operating system. Familiar with many other distributions as well.}
\vspace*{-2mm}
\cvitem{}{\dotfill}
\cvitem{Learning Goals:}{\emph{An ideal next role might involve some of
these concepts or technologies \textbf{(not limiting nor exhaustive)}}}
\cvitem{Ideas/Concepts}{Exposure to a broader array of cloud computing,
orchestration, and task management architectures, especially with focus on
concurrency and user interactability.}
\cvitem{Stacks/Languages}{\texttt{Rust}, \texttt{Scala},
\texttt{Go}, SaltStack, Databricks, Docker/Kubernetes, NoSQL, Headless BI}
\clearpage

% ------------------------------------------------------------------------------
% ---- Mathematics Experience
% ------------------------------------------------------------------------------
\section{Experience --- Mathematics}
\cventry{2017--2019}{Teaching Assistant}{Northwestern University}{Evanston,
IL}{}{Assisted professors of six multivariable and single-variable undergraduate
calculus classes by running discussion sections and working one-on-one with
students.}\nopagebreak
\cventry{2017--2018}{Peer Tutor}{Northwestern University}{Evanston,
IL}{}{Assisted fellow undergraduates of Northwestern University with a variety
of math courses in a weekly, drop-in setting.}\nopagebreak
\cventry{Summer 2017}{Independent Research in Math}{Northwestern
    University}{Evanston, IL}{}{Developed a concept of \emph{mathematical
        fragility} in birth and death stochastic processes.
\begin{itemize}
    \item   Used \texttt{Python} and accompanying analytical tools to develop a
        preliminary model through simulation of birth and death stochastic
        processes.
    \item   Mathematically analyzed examples to verify properties of these
        preliminary models.
    \item   Abstractly developed these preliminary models using mathematical
        tools from probability to draw out quantities that describe the
        fragility of a process.
\end{itemize}}
% \cventry{Fall 2016}{Research Assistant}{Northwestern University}{Evanston,
% IL}{}{Aided research on inquiry-based approaches to math education by recording
% classes and documenting student interactions in a novel classroom setting.}
% \subsection{Miscellaneous}
% \cventry{Summer 2016}{Research Assistant}{University of California San
% Diego}{San Diego, CA}{}{Developed a reusable analysis pipeline for single-cell
%     RNA sequencing data used in research on middle-ear infections.
% \begin{itemize}
%     \item   Worked with the \texttt{R} programming language to analyze data sets
%         for intuitive groupings.
%     \item   Wrote a series of scripts designed to process and analyze data sets
%         to look for differences in groupings.
%     \item   Created visualizations of data in order to better understand the
%         differences between these groups.
% \end{itemize}}

% ------------------------------------------------------------------------------
% ---- Education Section
% ------------------------------------------------------------------------------ 
\section{University \& Education}
\cventry{2015--2019}{Mathematics}{Northwestern University}{Evanston, IL}{GPA:
$3.7/4.0$}{Undergraduate major in Math with emphasis on advanced classes where
    possible.\newline Relevant Courses:
\begin{itemize}
    \item   \emph{ISP Math} --- A three quarter intensive course covering
        multivariable calculus, ordinary differential equations, and linear
        algebra.
    \item	  \emph{Foundations of Higher Math} --- A single quarter course on the
        standards of mathematical proof.
    \item	  \emph{MENU Real Analysis} --- A three quarter intensive course that
        rigorously develops calculus, including measure theory.
    \item	  \emph{MENU Abstract Algebra \& Abstract Algebra} --- Two quarters of
        an intensive course devoted to the study of groups and rings, followed
        by a one quarter course on Galois Theory.
    \item   \emph{Other Computer Science \& Applied Math} --- Various computer
        science and applied math courses covering topics including data
        structures, \texttt{Python} implementations of fundamental algorithms
        from machine learning, and computational neuronal modeling.
\end{itemize}}
\cventry{}{Music Technology}{Northwestern University}{Evanston,
IL}{}{Undergraduate minor in Music Technology, with coursework focused on
synthesis and analysis of electronic music. In a degree project, co-designed and
prototyped a laser harp digital music interface.}
\cventry{2011--2015}{High School Diploma}{Pacific Ridge School}{Carlsbad,
CA}{GPA: $4.0/4.0$}{}

% ------------------------------------------------------------------------------
% ---- Awards 
% ------------------------------------------------------------------------------
\section{Awards}
\cventry{May 2016}{Excellence in Mathematics by a First-Year
Student}{Northwestern University}{Evanston, IL}{}{Award given to students who
display strong achievement in a number of advanced mathematics courses offered
at Northwestern University.}
\cventry{May 2019}{Certificate of Recognition for Service as an Undergraduate
Teaching Assistant}{Northwestern University}{Evanston, IL}{}{A certificate given
to senior teaching assistants who dedicated their distinguished skills by
continually serving Northwestern's math department.}


% ------------------------------------------------------------------------------
% ---- Hobbies Section
% ------------------------------------------------------------------------------
\section{Hobbies and Interests}
\cvitem{Radio DJ}{Former on-air host of \textit{Non-Euclidean Space},
\textit{Excitotoxicity}, and \textit{Late Night Geometries} on WNUR 89.3 FM
Evanston-Chicago, with focus on electronic music of different geometries.}
\cvitem{MTG}{Have played the trading card game \textit{Magic: The Gathering} at
a competitive level.}
\cvitem{Cooking}{In the kitchen, a devotee of \emph{Good Eats}'s Alton Brown and
publications \emph{Serious Eats} and \emph{Cook's Illustrated}.}

